Integrating brain and biomechanical models - a new paradigm for understanding neuro-muscular control

### 2017-11-20 papers/integration/omm_integ.tex
Adds eye screen figures

% KM
\rvwt{An illustration of the biomechanical eye model is given in
Figure \ref{fig:eye_muscles}, while Figure \ref{fig:eye_head} depicts
the head model used in the proposed framework.}

% To be moved in due course
\begin{figure}[htb!]
\begin{center}
\includegraphics[width=0.5\textwidth]{./figures/bio_eye1.png}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:eye_muscles} Figure \arabic{figure}.}
{Example of the biomechanical eye model.}
\end{figure}

\begin{figure}[htb!]
\begin{center}
\includegraphics[width=0.5\textwidth]{./figures/bio_eye2.png}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:eye_head} Figure \arabic{figure}.}
{Example of the head model used.}
\end{figure}

@@

% KM
\rvwt{Figure \ref{fig:eye_sim0} illustrates an example of the experimental
set-up of the proposed framework, while Figures \ref{fig:eye_sim1}
and \ref{fig:eye_sim2} depict the developed eye oculomotor simulation
system.}

% Figures to merge together into a single panel or move.
\begin{figure}[htb!]
\begin{center}
\includegraphics[width=0.5\textwidth]{./figures/Eye_sim0.png}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:eye_sim0} Figure \arabic{figure}.}
{Example of the experimental set-up.}
\end{figure}

\begin{figure}[htb!]
\begin{center}
\includegraphics[width=0.5\textwidth]{./figures/Eye_sim1.png}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:eye_sim1} Figure \arabic{figure}.}
{Example of the eye simulator system.}
\end{figure}

\begin{figure}[htb!]
\begin{center}
\includegraphics[width=0.5\textwidth]{./figures/Eye_sim2.png}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:eye_sim2} Figure \arabic{figure}.}
{Example of use of the eye simulator system.}
\end{figure}

@@

>>>>

% KM
\rvwt{An illustration of the biomechanical eye model is given in
Figure \ref{fig:bioeye}, while Figure \ref{fig:bioeye} depicts
the head model used in the proposed framework.}

@@

@@

\begin{figure}[htb!]
\begin{center}
\includegraphics[width=0.5\textwidth]{./figures/eye_screen_plus.png}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:bioeye} Figure \arabic{figure}.}
{ The biomechanical eye. a) an OpenSim rendering of a pair of
biomechanical eyes showing the positions of the extraocular
muscles. b) OpenSim rendering of biomechanical eye within a head
model c) Top-down schematic cross-sectional view of the biomechanical eye situated
within a spherical screen, with a horizontal rotation towards a
luminances at an angle of $-\theta_{y}$ about the $y$ axis, which
points up out of the page.}
\end{figure}
